---
---
title: "Match Analysis: SMU vs. #2 Nebraska (Sept 3, 2024)"
author: "Brianna Eubank"
date: "2026-09-04"
format: html
---

## Match Summary: SMU Stuns No. 2 Nebraska

On September 3, 2024, SMU swept No. 2 Nebraska in 3 sets (25-23, 25-21, 25-18) at Moody Coliseum. SMU outhit the Huskers .242 to .171 and held a major advantage in service aces (7-1).

### Team Box Score Overview

| Team | Kills | Errors | Total Attacks | Hitting % | Assists | Aces | Digs | Blocks | Points |
| :--- | :--- | :--- | :--- | :--- | :--- | :--- | :--- | :--- | :--- |
| **SMU** | 39 | 15 | 99 | .242 | 35 | 7 | 43 | 10.0 | 56.0 |
| **Nebraska** | 36 | 18 | 105 | .171 | 35 | 1 | 36 | 9.0 | 46.0 |

---

## Individual Stat Leaders

### Top Hitters & Attackers

| Player | Team | Kills | Errors | Attacks | Hitting % | Points |
| :--- | :--- | :--- | :--- | :--- | :--- | :--- |
| **Naya Shime** | SMU | 9 | 6 | 28 | .107 | 12.5 |
| **Maya Tabron** | SMU | 9 | 2 | 24 | .292 | 11.0 |
| **Merritt Beason** | Nebraska | 9 | 6 | 28 | .107 | 10.5 |
| **Andi Jackson** | Nebraska | 8 | 0 | 12 | .667 | 12.0 |
| **Natalie Foster** | SMU | 8 | 2 | 13 | .462 | 15.5 |
| **Harper Murray** | Nebraska | 6 | 5 | 22 | .045 | 7.5 |

### Playmakers & Net Defense Leaders

* **Assists Leaders:** Celia Cullen (SMU) — 29 assists | Bergen Reilly (Nebraska) — 31 assists
* **Block Leaders:** Nnedi Okammor (SMU) — 9 blocks | Andi Jackson (Nebraska) — 6 blocks
* **Ace Leader:** Natalie Foster (SMU) — 5 aces

---

## Match Visualizations

### Team Performance Comparison

```{r}
#| label: fig-team-stats
#| fig-cap: "SMU vs Nebraska: Team Box Score Comparison"
#| message: false
#| warning: false

library(ggplot2)

team_data <- data.frame(
  Team = rep(c("SMU", "Nebraska"), each = 4),
  Metric = rep(c("Kills", "Digs", "Blocks", "Aces"), times = 2),
  Count = c(39, 43, 10, 7, 36, 36, 9, 1)
)

ggplot(team_data, aes(x = Metric, y = Count, fill = Team)) +
  geom_col(position = "dodge", width = 0.6) +
  scale_fill_manual(values = c("SMU" = "#003366", "Nebraska" = "#D00000")) +
  theme_minimal(base_size = 13) +
  labs(
    title = "SMU vs. #2 Nebraska: Team Totals",
    subtitle = "September 3, 2024 Matchup",
    x = "",
    y = "Total",
    fill = "Team"
  ) +
  theme(plot.title = element_text(face = "bold"))
```

### Top Hitters: Kills vs. Hitting Percentage

```{r}
#| label: fig-top-hitters
#| fig-cap: "Top Offensive Performers Efficiency Breakdown"
#| message: false
#| warning: false

hitters <- data.frame(
  Player = c("Naya Shime", "Maya Tabron", "Natalie Foster", "Merritt Beason", "Andi Jackson", "Harper Murray"),
  Team = c("SMU", "SMU", "SMU", "Nebraska", "Nebraska", "Nebraska"),
  Kills = c(9, 9, 8, 9, 8, 6),
  HittingPct = c(0.107, 0.292, 0.462, 0.107, 0.667, 0.045)
)

ggplot(hitters, aes(x = HittingPct, y = Kills, color = Team, label = Player)) +
  geom_point(size = 5) +
  geom_text(vjust = -1, fontface = "bold", size = 3.5) +
  scale_color_manual(values = c("SMU" = "#003366", "Nebraska" = "#D00000")) +
  scale_x_continuous(labels = scales::percent_format(accuracy = 1), limits = c(0, 0.75)) +
  scale_y_continuous(limits = c(4, 11)) +
  theme_minimal(base_size = 12) +
  labs(
    title = "Top Hitters: Attack Volume vs. Efficiency",
    x = "Hitting Percentage",
    y = "Kills"
  )
```